---
title: "Week 4 Part 1"
author: "Ruby Harris-Gavin"
date: "11/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Confidence intervals

```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43)

t.test(otter_length)
```

The mean length of sea otters is 42.22 inches with an sd of blah, and the 95% confidence interval is 34.69 to 49.75.

That's what this is saying - but when you look at the first part of the data, it is running this on a null value equal to 0. Obviously it is extremely unlikely that otter length of a random sample is 0.

## 2. T-test (1-sample t-test)

See a claim: mean otter length is 50 inches
I want to change the null hypothesis to equal 50, not 0.

```{r}
otter_test <- t.test(x = otter_length, mu = 50)
otter_test
```

SO what does 0.0444 mean? If the pop mean really is 50 inches, then there is a 4.44% chance that we could have taken a random sample from the population that has a mean that is at least as different from 50 as it is from our sample in either direction. 

## Two-sample t-test

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x = desert_bighorns, y = sierra_bighorns)
```

This uses a Welch's two sample t-test, which doesn't assume variance

